### 2020-05-31 system-model.tex
:construction: Fix iteration index
:ambulance: Fix contribution from information waveform

\input{info.tex}
\input{packages.tex}
\input{commands.tex}

@@

				& = \frac{3}{4}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{(h_{k,{n_1}}w_{I,{n_1}})(h_{k,{n_2}}w_{I,{n_2}})(h_{k,{n_3}}w_{I,{n_3}})^*(h_{k,{n_4}}w_{I,{n_4}})^*}\\
				& = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* = \frac{3}{4}\sum_{n=-N+1}^{N-1}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^*\\

@@

				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{I,n}^*\boldsymbol{h}_k)^* + (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^* \right)\nonumber\\

@@

				& \quad+ \frac{3}{8}\beta_4\rho^2\sum_{n=-N+1}^{N-1}\left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)(\boldsymbol{w}_I^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_I)^* + (\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\

@@

					&\quad+\frac{3}{8}{\beta_4}{\rho^2}\sum_{n=-N+1}^{N-1}{2t_{I,n}t_{I,n}^*+t_{P,n}t_{P,n}^*}\\

@@

					t_{I/P,n}^{(i)} (t_{I/P,n}^{(i)})^*
					& \approx 2 \Re\left\{t_{I/P,n}^{(i)} (t_{I/P,n}^{(i-1)})^*\right\} - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^* \\
					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\right\}\\
					& \quad - t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*\\
					& = \mathrm{Tr}\left((t_{I/P,n}^{(i-1)})^*\boldsymbol{C}_{I/P,n}\boldsymbol{\Phi}^{(i)}\right)\\
					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{(i-1)}\boldsymbol{C}_{I/P,n}^H\boldsymbol{\Phi}^{(i)}\right)\\
					& \quad- t_{I/P,n}^{(i-1)} (t_{I/P,n}^{(i-1)})^*
			and

@@

					& \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\\
					& = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\\
					& \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}

@@

					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)}) \\
					& \quad - \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{(i-1)} (t_{I,n}^{(i-1)})^* + t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \\

@@

					& \quad+ \frac{3}{8} \beta_4 \rho^2 \sum_{n=-N+1}^{N-1} 2\left((t_{I,n}^{(i-1)})^*\boldsymbol{C}_{I,n} + t_{I,n}^{(i-1)}\boldsymbol{C}_{I,n}^H\right)\\
					& \quad \quad + \left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\right)\\

@@

					&\quad+\frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1}{2t'_{I,n}t_{I,n}^{\prime \ *}+t'_{P,n}t_{P,n}^{\prime \ *}}\\

@@

					t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime \ (i)})^*
					& \approx 2 \Re\left\{t_{I/P,n}^{\prime \ (i)} (t_{I/P,n}^{\prime (i-1)})^*\right\} - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^* \\
					& = 2 \Re \left\{\mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\right\}\\
					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*\\
					& = \mathrm{Tr}\left((t_{I/P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{I/P}^{(i)}\right)\\
					& \quad + \mathrm{Tr}\left(t_{I/P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{I/P}^{(i)}\right)\\
					& \quad - t_{I/P,n}^{\prime (i-1)} (t_{I/P,n}^{\prime (i-1)})^*
			and
					t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime \ (i)}
					& \approx t_{I,0}^{\prime \ (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime \ (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\\
					& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I,0}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P,0}^{(i)})\\

@@

					& \quad - \frac{3}{8} \beta_4 \sum_{n=-N+1}^{N-1} 2t_{I,n}^{\prime (i-1)} (t_{I,n}^{\prime (i-1)})^* + t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\

@@

				& \quad + \frac{3}{4} \beta_4 \sum_{n=-N+1}^{N-1} (t_{I,n}^{\prime (i-1)})^*\boldsymbol{H}_{n}^* + t_{I,n}^{\prime (i-1)}\boldsymbol{H}_{n}^T\nonumber\\
				& \quad + \frac{3}{2} \beta_4 t_{P,0}^{\prime (i-1)}\boldsymbol{H}_{0}^*\label{eq:A_I}\\

@@

@@

			\begin{algorithm}
				\caption{Waveform Optimization}
				\label{alg:waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,\theta_l \ \forall l$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (k)} \forall n$ by \ref{eq:t'} for SCA
					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ for problem \ref{op:su_waveform} and corresponding $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}
	\end{subsection}
\end{section}

>>>>

\input{info.tex}
\input{packages.tex}

@@

				& = \frac{3}{4}\left(\sum_n{(h_{k,n}w_{I,n})(h_{k,n}w_{I,n})^*}\right)^2\\
				& = \frac{3}{4}(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)^2 = \frac{3}{4}(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)^2\\

@@

				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{h}_k^H\boldsymbol{W}_{I,0}^*\boldsymbol{h}_k)^2 + \sum_{n=-N+1}^{N-1} (\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)(\boldsymbol{h}_k^H\boldsymbol{W}_{P,n}^*\boldsymbol{h}_k)^*\right)\nonumber\\

@@

				& \quad+ \frac{3}{8}\beta_4\rho^2 \left(2(\boldsymbol{w}_I^H\boldsymbol{H}_{k,0}^*\boldsymbol{w}_I)^2 + \sum_{n=-N+1}^{N-1}(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)(\boldsymbol{w}_P^H\boldsymbol{H}_{k,n}^*\boldsymbol{w}_P)^* \right)\nonumber\\

@@

					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2t_{I,0}^2 + \sum_{n=-N+1}^{N-1}{t_{P,n}t_{P,n}^*}\right)\\

@@

				(t_{I,0}^{(i)})^2
				& \ge 2 (t_{I,0}^{(i)})(t_{I,0}^{(i-1)}) - (t_{I,0}^{(i-1)})^2\nonumber\\
				& = 2 \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) - (t_{I,0}^{(i-1)})^2\label{eq:t_approx_1}\\
				t_{P,n}^{(i)} (t_{P,n}^{(i)})^*
				& \ge 2 \Re\left\{t_{P,n}^{(i)} (t_{P,n}^{(i-1)})^*\right\} - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
				& = 2 \Re \left\{\mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\right\}\nonumber\\
				& \quad - t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\nonumber\\
				& = \mathrm{Tr}\left((t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n}\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
				& \quad + \mathrm{Tr}\left(t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H\boldsymbol{\Phi}^{(i)}\right)\nonumber\\
				& \quad- t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^*\label{eq:t_approx_2}\\

@@

				& \approx t_{I,0}^{(i)} t_{P,0}^{(i-1)} + t_{I,0}^{(i-1)} t_{P,0}^{(i)} - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\nonumber\\
				& = \mathrm{Tr}(t_{P,0}^{(i-1)}\boldsymbol{C}_{I,0}\boldsymbol{\Phi}^{(i)}) + \mathrm{Tr}(t_{I,0}^{(i-1)}\boldsymbol{C}_{P,0}\boldsymbol{\Phi}^{(i)})\nonumber\\
				& \quad - t_{I,0}^{(i-1)} t_{P,0}^{(i-1)}\label{eq:t_approx_3}
			Note that \ref{eq:t_approx_1} and \ref{eq:t_approx_2} provide lower bounds to convex terms $t_{I,0}^2$ and $t_{P,n} t_{P,n}^*$, but \ref{eq:t_approx_3} is only an approximation to $t_{I,0} t_{P,0}$ which is non-convex. Therefore, the approximated current function at iteration $i$ is

@@

					& = \mathrm{Tr}(\boldsymbol{A}^{(i)}\boldsymbol{\Phi}^{(i)})\\
					& \quad - \frac{3}{8} \beta_4 \rho^2 \left(2 (t_{I,0}^{(i-1)})^2 + \sum_{n=-N+1}^{N-1} t_{P,n}^{(i-1)} (t_{P,n}^{(i-1)})^* \right)\\

@@

					& \quad+ \frac{3}{8} \beta_4 \rho^2 \Biggl(4 t_{I,n}^{(i-1)} \boldsymbol{C}_0\\
					& \quad \quad + \sum_{n=-N+1}^{N-1} (t_{P,n}^{(i-1)})^*\boldsymbol{C}_{P,n} + t_{P,n}^{(i-1)}\boldsymbol{C}_{P,n}^H \Biggl)\\

@@

					&\quad+\frac{3}{8}{\beta_4}{\rho^2} \left(2(t'_{I,0})^2 + \sum_{n=-N+1}^{N-1}{t'_{P,n}(t'_{P,n})^*}\right)\\

@@

				(t_{I,0}^{\prime (i)})^2
				& \ge 2 \mathrm{Tr}\left(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}\right) - (t_{I,0}^{\prime (i-1)})^2\\
				t_{P,n}^{\prime (i)} (t_{P,n}^{\prime (i)})^*
				& \ge \mathrm{Tr}\left((t_{P,n}^{\prime (i-1)})^*\rho^{(i)}\boldsymbol{H}_{n}^*\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
				& \quad + \mathrm{Tr}\left(t_{P,n}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{n}^T\boldsymbol{W}_{P}^{(i)}\right)\nonumber\\
				& \quad - t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\\
				t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i)}
				& \approx t_{I,0}^{\prime (i)} t_{P,0}^{\prime (i-1)} + t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i)} - t_{I,0}^{\prime (i-1)} t_{P,0}^{\prime (i-1)}\nonumber\\
				& = \mathrm{Tr}(t_{P,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{I}^{(i)}) + \mathrm{Tr}(t_{I,0}^{\prime (i-1)}\rho^{(i)}\boldsymbol{H}_{0}^*\boldsymbol{W}_{P}^{(i)})\nonumber\\

@@

					& \quad - \frac{3}{8} \beta_4 \Biggl(2 (t_{I,0}^{\prime (i-1)})^2\\
					& \quad \quad + \sum_{n=-N+1}^{N-1} t_{P,n}^{\prime (i-1)} (t_{P,n}^{\prime (i-1)})^*\Biggl)\\

@@

				& = \frac{1}{2} \beta_2 \boldsymbol{H}_0^* + \frac{3}{2} \beta_4 (t_{I,0}^{\prime (i-1)} + t_{P,0}^{\prime (i-1)})\boldsymbol{H}_{0}^*\label{eq:A_I}\\

@@

				\addConstraint{\boldsymbol{W}_{I/P} \succeq 0}

@@

			\begin{algorithm}
				\caption{Waveform Optimization}
				\label{alg:waveform}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\bar{R},P,\theta_l \ \forall l$
					\State \textbf{Initialize} $i \leftarrow 0$, $\boldsymbol{W}_{I/P}^{(0)}$, $\rho^{(0)}$, $t_{I/P,n}^{\prime (0)} \ \forall n$
					\Repeat
					\State $i \leftarrow i + 1$
					\State Update SDR matrices $\boldsymbol{A}_{I/P}^{(i)}$ by \ref{eq:A_I} and \ref{eq:A_P}
					\State Obtain waveform matrices $\boldsymbol{W}_{I/P}^{(i)}$ and $\rho^{(i)}$ by solving problem \ref{op:su_waveform}
					\State Update auxiliary $t_{I/P,n}^{\prime (i)} \forall n$ by \ref{eq:t'} for SCA
					\Until $\lvert \tilde{z}^{(i)}-\tilde{z}^{(i-1)} \rvert \le \epsilon$
					\State Perform EVD $\boldsymbol{W}_{I/P}^{\star}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}^H$
					\State Generate random vectors $\boldsymbol{r}_q \ \forall q$ with entries uniformly distributed on the unit circle
					\State Construct candidate waveform vectors $\boldsymbol{w}_{I/P,r}=\boldsymbol{U}_{\boldsymbol{W}_{I/P}^{\star}}\boldsymbol{\Sigma}_{\boldsymbol{W}_{I/P}^{\star}}^{\frac{1}{2}}\boldsymbol{r}_q$ and corresponding matrices $\boldsymbol{W}_{I/P,q}=\boldsymbol{w}_{I/P,q}\boldsymbol{w}_{I/P,q}^H  \ \forall q$
					\State Select the best solution $\boldsymbol{W}_{I}^\star,\boldsymbol{W}_{P}^\star$ for problem \ref{op:su_waveform} and corresponding $\boldsymbol{w}_{I}^\star, \boldsymbol{w}_{P}^\star$
					\State \textbf{Output} $\boldsymbol{w}_I^\star, \boldsymbol{w}_P^\star, \rho^\star$
				\end{algorithmic}
			\end{algorithm}
		\end{subsubsection}
	\end{subsection}
\end{section}
